An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-26 poly-embed-journal/poly-embed-journal.tex
Adding the actual lemma statements in property translation subsection

In particular, consider the function $g$ so that $g$ and $f$ match on $\simplex$.

Define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$ for any $v \in \V$, and the set $\Theta := \{\theta(v) \mid v \in \V^*\}$.

@@

  Fix $p \in \simplex$.
  \begin{align*}
    p \in \theta(v)
    &\iff \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p} & \text{Def of $\theta$}\\
    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{p} & \text{Def of argmin}\\
    &\iff p \in \pi(F_v) & \text{Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}}
  \end{align*}

@@

\begin{claim}\label{claim:level-set-is-projected-face}
  For all $r \in \R$, take $v \in \V$ so that $v = L(r)$.
  $\Gamma_r = \theta(v) = \pi(F_{v}) \cap \simplex$.
\end{claim}
\begin{proof}
  % Follows immediately from Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
  Let us rewrite
  \begin{align*}
    \Gamma_r
    &= \{p \in \simplex \mid r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\}\\
    &= \{p \in \simplex \mid v \in \argmin_{v' \in \V} \inprod{v'}{p}\}\\
    &= \{p \in \simplex \mid \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p}\}\\
    &= \{p \in \simplex \mid \inprod{v}{p} = f(p) \}\\
    &= \theta(v)
  \end{align*}
  Now, we have $p \in \Gamma_r$ if and only if,
  \begin{align*}
    p \in \Gamma_r
    &\iff p \in \{p \in \simplex \mid \inprod{v}{p} = f(p)\} & \text{Definition of $\theta$}
    &\iff p \in \{p \in \simplex \mid \inprod{v}{p} = g(p)\} &\text {Since $f = g$ on simplex} \\
    &\iff p \in \{p \in \reals_+^\Y \mid \inprod{v}{p} = g(p)\} \cap \simplex &\text {Since $g$ defined over $\reals^\Y_+$} \\
    &\iff p \in \pi(F_v) \cap \simplex & \text{Following from definition of $F_v$}
  \end{align*}
  The result follows.

@@

% \begin{claim}
% 	For any $r \in \R$, take $v \in \V$ such that $v = L(r)$.
% 	$\theta(v) = \Gamma_r$.
% \end{claim}
% \begin{proof}
% 	\begin{align*}
% 	p \in \theta(v) &\iff \inprod{v}{p} = \min_{v' \in \V} \inprod{v'}{p}\\
% 	&\iff v \in \argmin_{v' \in \V} \inprod{v'}{p}\\
% 	&\iff r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\\ 
% 	&\iff p \in \Gamma_r
% 	\end{align*}
% \end{proof}

\jessie{Don't think this claim is actually necessary?}
\begin{corollary}
	$\Theta = \{\Gamma_r \mid r \in \R^*\}$ 
\end{corollary}
% \begin{proof}
% 	Fix $v \in \V^*$.
% 	By Corollary 9, there is some $r \in \R^*$ so that $v = L(r)$.
% 	\begin{align*}
% 	\theta(v) \in \Theta &\iff \inprod{v}{p} = \min_{v' \in \V} \inprod{v'}{p}\\
% 	&\iff r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\\
% 	&\iff r \in \argmin_{r' \in \R^*} \inprod{L(r')}{p}\\
% 	&\iff r \in \Gamma_r
% 	\end{align*}
% \end{proof}

\begin{claim}
	For any $r \in \R$, there exists a $v^* \in \V^*$ such that $\Gamma_r \subseteq \theta(v^*)$.\jessie{(7)}
\end{claim}
\begin{proof}
  Take $v = L(r)$.
  It suffices to show there is a $v^* \in \V$ such that $\theta(v) \subseteq \theta(v^*)$.
  We know $\theta(v) = \pi(F_v) \cap \simplex$ and similarly for $\theta(v^*)$ by Claim~\ref{claim:level-set-is-projected-face}.
  Moreover, we know that there is a $v^* \in \V^* \subseteq \V$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$ by Claim~\ref{claim:exists-vstar-projected-face-subset}.
  The result follows.
  % Let $v = L(r) \in \V$.
  % By Claim \ref{claim:vface-subset-some-vstar-face}, the face $F_v$ must be a subset of some $F_{v^*}$ for $v^* \in \V^*$.
  % We must then have $\pi(F_v) \cap \simplex = \Gamma_r \subseteq \pi(F_{v^*}) \cap \simplex = \theta(v^*)$.
\end{proof}

>>>>

\begin{corollary}\label{cor:f-matches-g-on-simplex}
  For all concave $f : \reals^{|\Y| + 1}_+ \to \reals_+ \cup \{-\infty\}$ with $\dom(f) = \simplex$, there is a polyhedral concave function $g : \reals^\Y_+ \to \reals_+$ with $\dom(g) = \reals^\Y_+$ so that $f(p) = g(p)$ for all $p \in \simplex$.
\end{corollary}
Given the function $f$, we consider $g$ to be such its extension and $L$ such that $\risk L_+ = g$ so that we may use the tools in Phases 1 and 2 draw conclusions about the property $\Gamma$.

Define the function $\theta(v) = \{p \in \simplex \mid \inprod{v}{p} = f(p)\}$ as the level sets of the loss vector $v \in \V$, and the set $\Theta := \{\theta(v) \mid v \in \V^*\}$ to be the set of (minimal) level sets uniquely defined by the loss vectors.

@@

  Fix $p \in \simplex$.
  \begin{align*}
    p \in \theta(v)
    &\iff \inprod{v}{p} = f(p) & \text{Def of $\theta$}\\
    &\iff \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p} & \text{$f$ matches $g$ on $\simplex$ (Cor.~\ref{cor:f-matches-g-on-simplex}.)}\\
    &\iff v \in \argmin_{v' \in \V}\inprod{v'}{p} & \text{Def of argmin}\\
    &\iff p \in \pi(F_v) & \text{Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}}
  \end{align*}

@@

\begin{claim}\label{claim:level-set-is-projected-face}
  For all $r \in \R$, take $v \in \V$ so that $v = L(r)$.
  $\Gamma_r = \theta(v) = \pi(F_{v}) \cap \simplex$.
\end{claim}
\begin{proof}
  % Follows immediately from Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}.
  Let us rewrite
  \begin{align*}
    \Gamma_r
    &= \{p \in \simplex \mid r \in \argmin_{r' \in \R} \inprod{L(r')}{p}\}\\
    &= \{p \in \simplex \mid v \in \argmin_{v' \in \V} \inprod{v'}{p}\}\\
    &= \{p \in \simplex \mid \inprod{v}{p} = \min_{v' \in \V}\inprod{v'}{p}\}\\
    &= \{p \in \simplex \mid \inprod{v}{p} = f(p) \}\\
    &= \theta(v)
  \end{align*}
  Now, we have $p \in \theta(v)$ if and only if,
  \begin{align*}
    p \in \theta(v)
    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = f(p')\} & \text{Definition of $\theta$}\\
    &\iff p \in \{p' \in \simplex \mid \inprod{v}{p'} = g(p')\} &\text {Since $f = g$ on simplex} \\
    &\iff p \in \{p' \in \reals_+^\Y \mid \inprod{v}{p'} = g(p')\} \cap \simplex &\text {Since $g$ defined over $\reals^\Y_+$} \\
    &\iff p \in \pi(F_v) \cap \simplex & \text{Following from definition of $F_v$}
  \end{align*}
  The result follows.

@@

\jessie{Don't think this claim is actually necessary?}
\begin{corollary}
	$\Theta = \{\Gamma_r \mid r \in \R^*\}$ 
\end{corollary}

\begin{claim}\label{claim:any-levelset-contained-in-minlevelset}
  For any $r \in \R$, there exists a $v^* \in \V^*$ such that $\Gamma_r \subseteq \theta(v^*)$.\jessie{(7)}
\end{claim}
\begin{proof}
  Take $v = L(r)$.
  It suffices to show there is a $v^* \in \V$ such that $\theta(v) \subseteq \theta(v^*)$ by their equality in Claim~\ref{claim:level-set-is-projected-face}.

  By Claim~\ref{claim:exists-vstar-projected-face-subset}, there is a $v^* \in \V^* \subseteq \V$ such that $\pi(F_v) \subseteq \pi(F_{v^*})$.
  Therefore, $\pi(F_v) \cap \simplex \subseteq \pi(F_{v^*})\cap \simplex$.  
  We know $\theta(v) = \pi(F_v) \cap \simplex$ and similarly for $\theta(v^*)$ by Claim~\ref{claim:level-set-is-projected-face}.
  The result follows.
  % Let $v = L(r) \in \V$.
  % By Claim \ref{claim:vface-subset-some-vstar-face}, the face $F_v$ must be a subset of some $F_{v^*}$ for $v^* \in \V^*$.
  % We must then have $\pi(F_v) \cap \simplex = \Gamma_r \subseteq \pi(F_{v^*}) \cap \simplex = \theta(v^*)$.
\end{proof}

\raf{From notes 6/21/2021}
\begin{itemize}
\item REP $\iff$ $\V^* \subseteq \V' := L(\R')$\jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}}
\item REP $\iff \jessie{\Lambda := \{\pi(F_v) \mid v \in \V^*\}; \Lambda \subseteq \{ \pi(F_{v}) \mid v \in L(\R')\}}$.
  \jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}}
\item $\Lambda$ == Full-dim \jessie{Claim~\ref{claim:projected-Vstar-faces-full-dim}.}
\item Lev sets subset $\theta$ \jessie{Just work with $\pi(F_{v})$ where $v \in L(\R)$}\jessie{Claim~\ref{claim:any-levelset-contained-in-minlevelset}}
\end{itemize}

\begin{claim}\label{claim:projected-faces-cover-RY-iff-representative}
  A set $\R' \subseteq \R$ with $\V' := L(\R')$ is representative for $L$ if and only if $\cup_{v \in \V'} \pi(F_v) = \reals^\Y_+$.  
\end{claim}
\begin{proof}
\jessie{TODO}  
\end{proof}

\begin{claim}
  \jessie{(1)}
  A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\V^* \subseteq \V'$.
\end{claim}
\begin{proof}
 Chain Claim~\ref{claim:projected-faces-cover-RY-iff-representative} and Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime} to yield the result.
\end{proof}

\begin{claim}
  \jessie{(3)}
  A finite set $\R' \subseteq \R$ with $\V' = L(\R')$ is representative if and only if $\Theta \subseteq \{\theta(v) \mid v \in \V'\}$.
\end{claim}
\begin{proof}
Chain Claim~\ref{claim:projected-faces-cover-RY-iff-representative} and Claim~\ref{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets} to yield the result.
\end{proof}

\begin{claim}
  \jessie{(6)}
  The set of full-dimensional level sets of $\Gamma$ is exactly $\Theta$.
\end{claim}
\begin{proof}
  From Claim~\ref{claim:projected-Vstar-faces-full-dim}, we know $\Lambda$ is exactly the set of full-dimensional level sets in $\reals^\Y_+$.
  Each element of $\Lambda$ is $\pi(F_v)$ for some $v \in \V^*$.
  Take $r \in \R^*$ so that $v = L(r)$.
  By Claim~\ref{claim:level-set-is-projected-face}, we have $\theta(v) = \Gamma_r = \pi(F_v) \cap \simplex$ is full-dimensional relative to the simplex.
  The result follows.
\end{proof}
